---
params:
  workingDir    : "in/"
title: "MultiGWAS Report "
output: 
  html_document:
    theme: cerulean
    toc: true
    number_sections: false
---

```{r include=FALSE,echo=FALSE}
library(knitr)
library(kableExtra)
```

```{r  echo=FALSE, message=FALSE}
inputDir     = paste0 (params$workingDir, "/report/")
```

```{r includeKnit, include=FALSE,echo=FALSE}
library(knitr)
library(kableExtra)
```

```{r setKnitOptions, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE)
cachedata = FALSE
cachemodels = FALSE
```

# INPUT PARAMETERS
```{r printTableInputParameters }
paramsDF = read.table (file=paste0(inputDir,"out-multiGWAS-inputParameters.tbl"), header=T, sep="\t")
kable (paramsDF) %>%
 	kable_styling(bootstrap_options = c("striped", "hover", "condensed", font_size=5))
```

# N BEST RANKED SNPs
Venn diagram and table showing the N best ranked SNPs found by each tool and by more than one tool.

## Venn diagram N best ranked SNPs
```{r vennDiagramBest, fig.align = "center", echo=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.fullwidth=TRUE}
knitr::include_graphics (paste0(inputDir,"/out-multiGWAS-vennDiagram-best.png"))
```

## Table N best ranked SNPs
```{r printTableBest,  echo=FALSE, message=FALSE}
bestTable = read.table (file=paste0(inputDir, "/out-multiGWAS-scoresTable-best.scores"), header=T, sep="\t")
kable (bestTable) %>%
 	kable_styling(bootstrap_options = c("striped", "hover", "condensed", font_size=5))
```

# SIGNIFICATIVE SNPs
Venn diagram and table showing the signficative SNPs found by each tool and by more than one tool.

## Venn diagran signficative SNPs
```{r, fig.align = "center", echo=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.fullwidth=TRUE}
knitr::include_graphics (paste0 (inputDir,"/out-multiGWAS-vennDiagram-significatives.png"))
```

## Table significative SNPs
```{r  echo=FALSE, message=FALSE}
significativesTable = read.table (file=paste0(inputDir, "/out-multiGWAS-scoresTable-significatives.scores"), header=T, sep="\t")
kable (significativesTable) %>%
 	kable_styling(bootstrap_options = c("striped", "hover", "condensed", font_size=5))
```

# MANHATTAN AND QQ PLOTS
Manhattan and QQ plots for the GWAS analysis of the four tools. 

 - The SNPs above the red line were found as significatives for each tool
 - The SNPs above the blue line correspond to the N best ranked SNPs for each tool
 - SNPs marked in green were found by more than one tool.
```{r  fig.widht=11, fig.height=30, fig.fullwidth=TRUE}
knitr::include_graphics (paste0 (inputDir, "/out-multiGWAS-manhattanQQ-plots.png"))
```
